%\bibliographystyle{babplain-uh}
%\bibliography{Bibliography}
\begin{thebibliography}{99}
	
\bibitem{arnoldi} Arnoldi W.E.: The principle of minimized iterations in the solution of the matrix eigenvalue
problem. Quarterly of Applied Mathematics, 9(1):17–29, 1951.

\bibitem{allenchan2d} Bates P.W., Brown S., Han J.: Numerical analysis for a nonlocal Allen-Cahn
equation. International Journal of Numerical Analysis and Modeling, 6(1):33–49, 2009.

\bibitem{IntroMatrix} Bellman R.: Introduction to matrix analysis, volumen 19. SIAM, 1997.

\bibitem{Berland07} Berland H., Skaflestad B., Wright W.M.: EXPINT A MATLAB package for exponential
integrators. ACM Transactions on Mathematical Software (TOMS), 33(1):4, 2007.

\bibitem{newtonkry} Brown P.N., Walker H.F., Wasyk R., Woodward C.S.: On using approximate
finite differences in matrix-free Newton–Krylov methods. SIAM Journal on Numerical Analysis,
46(4):1892–1911, 2008.

\bibitem{numerical} Burden R.L., Faires J.D.: Numerical Analysis. Cengage Learning, 9th edición,
2010.

\bibitem{carr11} Carr E.J., Moroney T.J., Turner I.W.: Efficient simulation of unsaturated flow
using exponential time integration. Applied Mathematics and Computation, 217(14):6587–6596,
2011.

\bibitem{delaCruz06} de la Cruz H., Biscay R.J., Carbonell F., Jiménez J.C., Ozaki T.: Local
Linearization-Runge Kutta (LLRK) methods for solving ordinary differential equations. En
International Conference on Computational Science, páginas 132–139. Springer, 2006.

\bibitem{delaCruz07} de la Cruz H., Biscay R.J.,  Carbonell F., Ozaki T., Jiménez J.C.: A higher
order Local Linearization method for solving ordinary differential equations. Applied Mathematics
and Computation, 185(1):197–212, 2007.

\bibitem{Jimenez13} de la Cruz H., Biscay R.J., Jiménez J.C., Carbonell F.: Local
linearization—Runge–Kutta methods: a class of A-stable explicit integrators for dynamical systems.
Mathematical and Computer Modelling, 57(3-4):720–740, 2013.

\bibitem{cusp1} Fitz R.: Mathematical models of excitation and propagation in nerve. Biological
engineering, páginas 1–85, 1969.

\bibitem{Golub96} Golub G.H., Van Loan C.F.: Matrix Computation. The Johns Hopkins University Press, 3th ed., 1996.

\bibitem{grayscott2d} Gray P., Scott S.K.: Autocatalytic reactions in the isothermal, continuous stirred tank reactor:
Oscillations and instabilities in the system $A+2B\to 3B,\, B\to C$. Chemical Engineering Science,
39(6):1087–1097, 1984.

\bibitem{Hairer-Wanner96} Hairer E., Wanner G.: Solving Ordinary Differential Equations II. Stiff and Differential-
Algebraic Problems. Springer Series in Computational Mathematics. Springer-Verlag, Berlin,
3th ed., 1996.

\bibitem{expode} Hochbruck M., Jansing G.: Advanced Exponential Time Integration Toolbox for MATLAB, 2015.

\bibitem{hoch97} Hochbruck M., Lubich C.: On Krylov subspace approximations to the matrix exponential
operator. SIAM Journal on Numerical Analysis, 34(5):1911–1925, 1997.

\bibitem{hochbruck1998exponential} Hochbruck M., Lubich C., Selhofer H.: Exponential integrators for large systems
of differential equations. SIAM Journal on Scientific Computing, 19(5):1552–1574, 1998.

\bibitem{adams} Hochbruck M., Ostermann A.: Exponential multistep methods of Adams-type. BIT
Numerical Mathematics, 51(4):889–908, 2011.

\bibitem{ross} Hochbruck M., Ostermann A., Schweitzer J.: Exponential Rosenbrock-type methods.
SIAM Journal on Numerical Analysis, 47(1):786–803, 2009.

\bibitem{hysom2002level} Hysom D., Pothen A.: Level-based incomplete LU factorization: Graph model and algorithms.
Preprint UCRL-JC-150789, US Department of Energy, Nov, 2002.

\bibitem{matrixexp} Jennings A.: Matrix computation for engineers and scientists. London and New York,
Wiley-Interscience, 1977. 340 p, 1977.

\bibitem{Jimenez02AMC} Jiménez J.C, Biscay R., Mora C., Rodriguez L.M.: Dynamic properties of the
Local Linearization method for initial-value problems. Applied Mathematics and Computation,
126(1):63–81, 2002.

\bibitem{Jimenez05AMC} Jiménez J.C., Carbonell F. : Rate of convergence of Local Linearization schemes for initial value
problems. Applied Mathematics and Computation, 171(2):1282–1295, 2005.

\bibitem{Jimenez14AMC} Jiménez J.C., Sotolongo A., Sanchez-Bornot J.M.: Locally Linearized Runge-Kutta
method of Dormand and Prince. Applied Mathematics and Computation, 247:589–606, 2014.

\bibitem{errorpade} Jimenez J.C., de la Cruz H.: Convergence rate of strong Local Linearization
schemes for stochastic differential equations with additive noise. BIT Numerical Mathematics,
52(2):357–382, 2012. (Citado en las páginas 10 y 14).

\bibitem{freej} Knoll D.A., Keyes D.E.: Jacobian-free Newton–Krylov methods: a survey of approaches
and applications. Journal of Computational Physics, 193(2):357–397, 2004.

\bibitem{bruss} Lefever R., Nicolis G.: Chemical instabilities and sustained oscillations. Journal of
Theoretical Biology, 30(2):267–284, 1971.

\bibitem{loffeld2013comparative} Loffeld J., Tokman M.: Comparative performance of exponential, implicit, and explicit
integrators for stiff systems of ODEs. Journal of Computational and Applied Mathematics,
241:45–67, 2013.

\bibitem{VanLoan03} Moler C., Van Loan C. : Nineteen dubious ways to compute the exponential of a matrix,
twenty-five years later. SIAM Review, 45(1):3–49, 2003.

\bibitem{cusp2} Nagumo J.,Arimoto S., Yoshizawa S.: An active pulse transmission line simulating
nerve axon. Proceedings of the IRE, 50(10):2061–2070, 1962.

\bibitem{phi} Niesen J., Wright W.M.: A Krylov subspace algorithm for evaluating the $\phi$-functions
appearing in exponential integrators. ACM, 2009.

\bibitem{pope} Pope D.A.: An exponential method of numerical integration of ordinary differential equations.
Communications of the ACM, 6(8):491–493, 1963.

\bibitem{Saad92} Saad Y.: Analysis of some Krylov subspace approximations to the matrix exponential operator.
SIAM Journal on Numerical Analysis, 29(1):209–228, 1992.

\bibitem{saad2003iterative} Saad Y.: Iterative methods for sparse linear systems, Volumen 82. SIAM, 2003.

\bibitem{Shampine} Shampine L.F., Reichelt M.W.: The Matlab ODE suite. SIAM J. Sci. Comput., 18:11–22,
1997.

\bibitem{dnd} Sherratt J.A.: On the form of smooth-front travelling waves in a reaction-diffusion equation
with degenerate nonlinear diffusion. Mathematical Modelling of Natural Phenomena, 5(5):64–
79, 2010.

\bibitem{Sidje98} Sidje R.B.: Expokit: A software package for computing matrix exponentials. ACM Transactions
on Mathematical Software (TOMS), 24(1):130–156, 1998.

\bibitem{shampinepde} Sommeijer, B.P., Shampine L.F., Verwer J.G.: RKC: An explicit solver for parabolic PDEs.
Journal of Computational and Applied Mathematics, 88:315–326, 1997.

\bibitem{Sotolongo11} Sotolongo A.: Construcción y estudio de códigos adaptativos de Linealización Local. Tesis de
Grado. Universidad de La Habana, 2011.

\bibitem{Sotolongo14} Sotolongo A., Jiménez J.C.: Construction and study of Local Linearization adaptive codes
for ordinary differential equations. Revista de Matemática: Teoría y Aplicaciones, 21(1):21–53,
2014.

\bibitem{tokman} Tokman M.: Efficient integration of large stiff systems of ODEs with exponential propagation
iterative (EPI) methods. Journal of Computational Physics, 213(2):748–776, 2006.

\bibitem{cusp3} Zeeman E.C.: Differential equations for the heart beat and nerve impulse, in “Towards a Theoretical
Biology,” Vol. 4. Edinburgh Univ. Press, Edingburgh, páginas 8–67, 1972.

\bibitem{zou2016} Zou L., Zhao H., Zhang H.: Solving Phase Appearance/Disappearance Two-Phase
Flow Problems with High Resolution Staggered Grid and Fully Implicit Schemes by Jacobian-
Free Newton-Krylov Method. Computers and Fluids, 2016.
	
\end{thebibliography}